---
title       : Reproducible Pitch
subtitle    : Production for Coursera assignement (Course 9 - Week 4)
author      : Idriss . S
job         : 
framework   : revealjs        # {io2012, html5slides, shower, dzslides, ...}
revealjs    : {theme: moon, transition: cube}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets : {rCharts: [libraries/nvd3]}
---


</br></br></br>

# Reproducible Pitch
## Production for Coursera assignement (Course 9 - Week 4)
#### Author : Idriss .S
#### Date : 12 april 2022

--- &vertical

### Introduction

This presentation aims to study a data set from R : `ToothGrowth`.

It's cover :

1. only data exploration (due to the limitation of 5 slides) ;

</br>

This work could be completed (of more slides are allowed) by :

2. fitting model responding to the question that try to explain the relationship 
between miles per gallon consmption and weight for each car.
3. discussions

</br>

### Exploratory data analysis

#### Data structure

```{r} 
data(ToothGrowth)
str(ToothGrowth)
```

***

#### Data structure - 2
```{r mesage=F}
library(tidyr)
library(rstatix)
ToothGrowth %>% sample_n_by(dose, size = 3)
# Quick summary of the data
summary(ToothGrowth)
# Exploration of ToothGrowth$dose and ToothGrowth$len, since we know exactly what ToothGrowth$supp contains
unique(ToothGrowth$dose)
unique(ToothGrowth$len)
```

***

#### Box plot - code


```{r plot_1}
library(ggplot2)
my_plot_fun <- function(my_data,my_x) {
  my_data <- as.data.frame(my_data)
  my_data %>%
  ggplot(aes(x=my_x, y=len)) +
theme(plot.title = element_text(color="#ADA717", size=18, face="bold.italic",hjust=0.5),
 axis.title.x = element_text(color="#993333", size=18, face="bold"),
 axis.text.x = element_text(color="#993333", size=14,vjust = 0),
 axis.title.y = element_text(color="darkgreen", size=18, face="bold"),
 axis.text.y = element_text(face="bold", color="darkgreen", size=14),
 legend.text = element_text(size=12),
 legend.title = element_text(size=16))}

# Conversion of ToothGrowth$dose into a factor
ToothGrowth$dose<-as.factor(ToothGrowth$dose)

mpt <-my_plot_fun(ToothGrowth,my_x = ToothGrowth$dose) + 
  geom_boxplot(aes(color = supp,group=dose), width = 0.6) +
  geom_dotplot(aes(fill = as.factor(dose), color = supp,group=dose), binaxis='y', stackdir='center', 
               dotsize = 0.8,position = position_dodge(0.8),binwidth=1)+
  scale_fill_manual( values = c("#00AFBB", "#E3B166","#A1A861"))+
  scale_color_manual(values = c("red", "black")) + facet_grid(~ supp)+
  labs(x = "Doses", y ="Toothe Length", fill = "Doses", color="Supplement delivery",
    title = "Tooth length \n by dose amount",
  caption = "Plot tooth length ('len') by the dose amount ('dose'), \n grouped by supplement delivery method ('supp')") +
  theme(plot.caption = element_text(color = "darkblue", face = "italic", size = 12))
```

***
#### Box plot - plot

```{r fig.width=15}
mpt
```

</br>

#### Thanks for watching. Regards.
##### Idriss .S